The title

### 2023-01-09 docs/draft/draft.Rmd
intro+teoria
Bibiografia arreglada

pero claro el esta lli @lee2022factors lkasla

@@

Language attitudes are key in the language learning environment, as they can determine the success of a student (e.g., Thompson, 2021). A learner with a positive attitude toward a learning environment will more likely succeed than a learner who finds the environment difficult or disengaged. Specifically, the attitudes in online learning have been shown to play a key role as students are physically detached from the learning environment, and rely more on self-regulation abilities (Alqurashi, 2016; Horvat et al., 2015; Ke & Kwak, 2013; Wurst et al., 2008). Within this framework, anxiety has been linked in several research studies (e.g., Teimouri et al., 2019) as an indicator of poor linguistic development. Interestingly, anxiety and the fear of the unknown is a feeling that fluctuates with empirical contact throughout the academic appointment. Furthermore, Webb et al. (2014) studied the attitudes of students and teachers in a flipped online classroom of Chinese. Their results showed an incremental fluctuation in their perception. That is, they found distance education would not meet student expectations at first, but through the semester they found a growing acceptance that led to successful results by the end of a 15-week term. A similar psychological development is observed in Ushida’s (2005) study which investigated the changes in students’ attitudes and motivation over time in online language courses. Their results showed a similar evolution within the student’s attitudes, as students reduced their anxiety level as the semester progressed, feeling more comfortable with the system as well as the teaching materials by the end of the educational term. 
Past educational experiences and abilities acquired through these experiences have an effect on how students shape attitudes toward a new learning encounter (Saito et al. 2018), as well as the familiarity and complexity of the instruments that the course requires (Heckel & Ringeisen, 2019), which might involve some training and assistance before the beginning of the online course. During the covid outbreak, students and educators lacked experience with online tools as well as time to prepare, Moser et al. (2021), leading to an overall feeling of less effective education Top hat (2020), Hodges et al. (2020), Lee (2021). While the immediate transition to online education seemed rushed in Ana Ruiz-Alonso-Bartol et al (YEAR) the stress levels of undergraduates diminished from the beginning to the end of the academic term as they became more familiar with the instructional materials, and therefore gained more experience with their newfound educational setting. Their study of US undergraduates found varied responses in which some students enjoyed the increased autonomy and self-paced learning opportunities offered by the new online format. Along the same line, a survey of university students found a common belief that online education helped them continue their education while still learning, observing, and improving the quality of teaching as their professors gained more experience with the teaching instruments Chakraborty et al. (2020). 
The outbreak of COVID-19 has caused online teaching and learning to evolve very rapidly during the past two years. This was a global phenomenon in the history of language education which had many educational consequences that students most likely will continue to experience when approaching online education. With a global decrease in Covid-19 cases, most US universities slowly began to switch to a pre-pandemic educational setting or blend hybrid classes. The goal of this paper is dual, first to determine if online education is still in demand among our undergraduate students, and to identify what are the attitudes towards it in a context where online education is no longer mandatory. Our second goal is to better understand how our new post-pandemic reality modulates tendencies in university language class enrollment.

@@

Our premise in this research study is to gather information from our current students who are in an educational environment that has been in continuous change for the past few years. The effects of this ever-changing learning environment have affected students and continue to affect the way they interact with and view their education. Post-pandemic effects, along with world socio-economic changes such as inflation and the need to work, have brought a new educational reality that affects tendencies toward language enrollment. To better understand these tendencies, we employed the lens of The Grounded Theory, as it allows a cyclical observation of a changing world. The Grounded Theory considers a changing environment that can evolve, becoming the researcher a constant observer of the changes produced (Hernández Carrera, 2014). Having a better understanding of the constant change of tendencies that affect our students can help us not only to provide them with adequate tools to succeed but also help us in providing courses that match their needs and expectations.

This theoretical approach allowed us to perform mixed models including qualitative, quantitative, and open questionary deriving the hypothesis we present in this paper. This approach was chosen as it allows the researcher to observe a constant change in tendencies and derive a hypothesis based on the collected data.  Due to the geographical limitations, we adopt a substantive Grounded Theory that helps explain the tendencies seen within our community of students and the factors that affect them (Corbin & Strauss, 2014).

>>>>

@@

Language attitudes are key in the language learning environment, as they can determine the success of a student [ eg @thompson2021attitudes]. A learner with a positive attitude toward a learning environment will more likely succeed than a learner who finds the environment difficult or disengaged. Specifically, the attitudes in online learning have been shown to play a key role as students are physically detached from the learning environment, and rely more on self-regulation abilities [ @alqurashi2016self; @horvat2015student; @ke2013constructs; @lan2010using]. Within this framework, anxiety has been linked in several research studies [e.g.,@teimouri2019second] as an indicator of poor linguistic development. Interestingly, anxiety and the fear of the unknown is a feeling that fluctuates with empirical contact throughout the academic appointment. Furthermore, @webb2014flipping studied the attitudes of students and teachers in a flipped online classroom of Chinese. Their results showed an incremental fluctuation in their perception. That is, they found distance education would not meet student expectations at first, but through the semester they found a growing acceptance that led to successful results by the end of a 15-week term. A similar psychological development is observed in @ushida2005role study which investigated the changes in students’ attitudes and motivation over time in online language courses. Their results showed a similar evolution within the student’s attitudes, as students reduced their anxiety level as the semester progressed, feeling more comfortable with the system as well as the teaching materials by the end of the educational term. 
Past educational experiences and abilities acquired through these experiences have an effect on how students shape attitudes toward a new learning encounter (Saito et al. 2018), as well as the familiarity and complexity of the instruments that the course requires (@heckel2019pride), which might involve some training and assistance before the beginning of the online course. During the covid outbreak, students and educators lacked experience with online tools as well as time to prepare, @tomasik2021educational, leading to an overall feeling of less effective education Top hat (2020), @hodges2020difference, @lee2022factors. While the immediate transition to online education seemed rushed in @ruiz2022transitioning the stress levels of undergraduates diminished from the beginning to the end of the academic term as they became more familiar with the instructional materials, and therefore gained more experience with their newfound educational setting. Their study of US undergraduates found varied responses in which some students enjoyed the increased autonomy and self-paced learning opportunities offered by the new online format. Along the same line, a survey of university students found a common belief that online education helped them continue their education while still learning, observing, and improving the quality of teaching as their professors gained more experience with the teaching instruments [@chakraborty2021opinion]. 
The outbreak of COVID-19 has caused online teaching and learning to evolve very rapidly during the past two years. This was a global phenomenon in the history of language education which had many educational consequences that students most likely will continue to experience when approaching online education. With a global decrease in Covid-19 cases, most US universities slowly began to switch to a pre-pandemic educational setting or blend hybrid classes. The goal of this paper is dual, first to determine if online education is still in demand among our undergraduate students, and to identify what are the attitudes towards it in a context where online education is no longer mandatory. Our second goal is to better understand how our new post-pandemic reality modulates tendencies in university language class enrollment.

@@

Our premise in this research study is to gather information from our current students who are in an educational environment that has been in continuous change for the past few years. The effects of this ever-changing learning environment have affected students and continue to affect the way they interact with and view their education. Post-pandemic effects, along with world socio-economic changes such as inflation and the need to work, have brought a new educational reality that affects tendencies toward language enrollment. To better understand these tendencies, we employed the lens of The Grounded Theory, as it allows a cyclical observation of a changing world. The Grounded Theory considers a changing environment that can evolve, becoming the researcher a constant observer of the changes produced [@hernandez2014investigacion]. Having a better understanding of the constant change of tendencies that affect our students can help us not only to provide them with adequate tools to succeed but also help us in providing courses that match their needs and expectations.

This theoretical approach allowed us to perform mixed models including qualitative, quantitative, and open questionary deriving the hypothesis we present in this paper. This approach was chosen as it allows the researcher to observe a constant change in tendencies and derive a hypothesis based on the collected data.  Due to the geographical limitations, we adopt a substantive Grounded Theory that helps explain the tendencies seen within our community of students and the factors that affect them [@corbin2014basics].

### 2023-01-09 docs/draft/draft.tex
intro+teoria
Bibiografia arreglada

pero claro el esta lli (\textbf{lee2022factors?}) lkasla

@@

Language attitudes are key in the language learning environment, as they can determine the success of a student (e.g., Thompson, 2021). A learner with a positive attitude toward a learning environment will more likely succeed than a learner who finds the environment difficult or disengaged. Specifically, the attitudes in online learning have been shown to play a key role as students are physically detached from the learning environment, and rely more on self-regulation abilities (Alqurashi, 2016; Horvat et al., 2015; Ke \& Kwak, 2013; Wurst et al., 2008). Within this framework, anxiety has been linked in several research studies (e.g., Teimouri et al., 2019) as an indicator of poor linguistic development. Interestingly, anxiety and the fear of the unknown is a feeling that fluctuates with empirical contact throughout the academic appointment. Furthermore, Webb et al.~(2014) studied the attitudes of students and teachers in a flipped online classroom of Chinese. Their results showed an incremental fluctuation in their perception. That is, they found distance education would not meet student expectations at first, but through the semester they found a growing acceptance that led to successful results by the end of a 15-week term. A similar psychological development is observed in Ushida's (2005) study which investigated the changes in students' attitudes and motivation over time in online language courses. Their results showed a similar evolution within the student's attitudes, as students reduced their anxiety level as the semester progressed, feeling more comfortable with the system as well as the teaching materials by the end of the educational term.
Past educational experiences and abilities acquired through these experiences have an effect on how students shape attitudes toward a new learning encounter (Saito et al.~2018), as well as the familiarity and complexity of the instruments that the course requires (Heckel \& Ringeisen, 2019), which might involve some training and assistance before the beginning of the online course. During the covid outbreak, students and educators lacked experience with online tools as well as time to prepare, Moser et al.~(2021), leading to an overall feeling of less effective education Top hat (2020), Hodges et al.~(2020), Lee (2021). While the immediate transition to online education seemed rushed in Ana Ruiz-Alonso-Bartol et al (YEAR) the stress levels of undergraduates diminished from the beginning to the end of the academic term as they became more familiar with the instructional materials, and therefore gained more experience with their newfound educational setting. Their study of US undergraduates found varied responses in which some students enjoyed the increased autonomy and self-paced learning opportunities offered by the new online format. Along the same line, a survey of university students found a common belief that online education helped them continue their education while still learning, observing, and improving the quality of teaching as their professors gained more experience with the teaching instruments Chakraborty et al.~(2020).
The outbreak of COVID-19 has caused online teaching and learning to evolve very rapidly during the past two years. This was a global phenomenon in the history of language education which had many educational consequences that students most likely will continue to experience when approaching online education. With a global decrease in Covid-19 cases, most US universities slowly began to switch to a pre-pandemic educational setting or blend hybrid classes. The goal of this paper is dual, first to determine if online education is still in demand among our undergraduate students, and to identify what are the attitudes towards it in a context where online education is no longer mandatory. Our second goal is to better understand how our new post-pandemic reality modulates tendencies in university language class enrollment.

@@

Our premise in this research study is to gather information from our current students who are in an educational environment that has been in continuous change for the past few years. The effects of this ever-changing learning environment have affected students and continue to affect the way they interact with and view their education. Post-pandemic effects, along with world socio-economic changes such as inflation and the need to work, have brought a new educational reality that affects tendencies toward language enrollment. To better understand these tendencies, we employed the lens of The Grounded Theory, as it allows a cyclical observation of a changing world. The Grounded Theory considers a changing environment that can evolve, becoming the researcher a constant observer of the changes produced (Hernández Carrera, 2014). Having a better understanding of the constant change of tendencies that affect our students can help us not only to provide them with adequate tools to succeed but also help us in providing courses that match their needs and expectations.

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-R-papaja}{}}%
Aust, F., \& Barth, M. (2022). \emph{{papaja}: {Prepare} reproducible {APA} journal articles with {R Markdown}}. Retrieved from \url{https://github.com/crsh/papaja}

@@

@@

>>>>

@@

Language attitudes are key in the language learning environment, as they can determine the success of a student (eg Thompson, 2021). A learner with a positive attitude toward a learning environment will more likely succeed than a learner who finds the environment difficult or disengaged. Specifically, the attitudes in online learning have been shown to play a key role as students are physically detached from the learning environment, and rely more on self-regulation abilities (Alqurashi et al., 2016; Horvat, Dobrota, Krsmanovic, \& Cudanov, 2015; Ke \& Kwak, 2013; Lan \& Sie, 2010). Within this framework, anxiety has been linked in several research studies (e.g., Teimouri, Goetze, \& Plonsky, 2019) as an indicator of poor linguistic development. Interestingly, anxiety and the fear of the unknown is a feeling that fluctuates with empirical contact throughout the academic appointment. Furthermore, Webb, Doman, and Pusey (2014) studied the attitudes of students and teachers in a flipped online classroom of Chinese. Their results showed an incremental fluctuation in their perception. That is, they found distance education would not meet student expectations at first, but through the semester they found a growing acceptance that led to successful results by the end of a 15-week term. A similar psychological development is observed in Ushida (2005) study which investigated the changes in students' attitudes and motivation over time in online language courses. Their results showed a similar evolution within the student's attitudes, as students reduced their anxiety level as the semester progressed, feeling more comfortable with the system as well as the teaching materials by the end of the educational term.
Past educational experiences and abilities acquired through these experiences have an effect on how students shape attitudes toward a new learning encounter (Saito et al.~2018), as well as the familiarity and complexity of the instruments that the course requires (Heckel and Ringeisen (2019)), which might involve some training and assistance before the beginning of the online course. During the covid outbreak, students and educators lacked experience with online tools as well as time to prepare, Tomasik, Helbling, and Moser (2021), leading to an overall feeling of less effective education Top hat (2020), Hodges, Moore, Lockee, Trust, and Bond (2020), Lee (2022). While the immediate transition to online education seemed rushed in Ruiz-Alonso-Bartol, Querrien, Dykstra, Fernández-Mira, and Sánchez-Gutiérrez (2022) the stress levels of undergraduates diminished from the beginning to the end of the academic term as they became more familiar with the instructional materials, and therefore gained more experience with their newfound educational setting. Their study of US undergraduates found varied responses in which some students enjoyed the increased autonomy and self-paced learning opportunities offered by the new online format. Along the same line, a survey of university students found a common belief that online education helped them continue their education while still learning, observing, and improving the quality of teaching as their professors gained more experience with the teaching instruments (Chakraborty, Mittal, Gupta, Yadav, \& Arora, 2021).
The outbreak of COVID-19 has caused online teaching and learning to evolve very rapidly during the past two years. This was a global phenomenon in the history of language education which had many educational consequences that students most likely will continue to experience when approaching online education. With a global decrease in Covid-19 cases, most US universities slowly began to switch to a pre-pandemic educational setting or blend hybrid classes. The goal of this paper is dual, first to determine if online education is still in demand among our undergraduate students, and to identify what are the attitudes towards it in a context where online education is no longer mandatory. Our second goal is to better understand how our new post-pandemic reality modulates tendencies in university language class enrollment.

@@

Our premise in this research study is to gather information from our current students who are in an educational environment that has been in continuous change for the past few years. The effects of this ever-changing learning environment have affected students and continue to affect the way they interact with and view their education. Post-pandemic effects, along with world socio-economic changes such as inflation and the need to work, have brought a new educational reality that affects tendencies toward language enrollment. To better understand these tendencies, we employed the lens of The Grounded Theory, as it allows a cyclical observation of a changing world. The Grounded Theory considers a changing environment that can evolve, becoming the researcher a constant observer of the changes produced (Hernandez Carrera, 2014). Having a better understanding of the constant change of tendencies that affect our students can help us not only to provide them with adequate tools to succeed but also help us in providing courses that match their needs and expectations.

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-alqurashi2016self}{}}%
Alqurashi, E. et al. (2016). Self-efficacy in online learning environments: A literature review. \emph{Contemporary Issues in Education Research (CIER)}, \emph{9}(1), 45--52.

\leavevmode\vadjust pre{\hypertarget{ref-R-papaja}{}}%
Aust, F., \& Barth, M. (2022). \emph{{papaja}: {Prepare} reproducible {APA} journal articles with {R Markdown}}. Retrieved from \url{https://github.com/crsh/papaja}

@@

\leavevmode\vadjust pre{\hypertarget{ref-chakraborty2021opinion}{}}%
Chakraborty, P., Mittal, P., Gupta, M. S., Yadav, S., \& Arora, A. (2021). Opinion of students on online education during the COVID-19 pandemic. \emph{Human Behavior and Emerging Technologies}, \emph{3}(3), 357--365.

\leavevmode\vadjust pre{\hypertarget{ref-corbin2014basics}{}}%
Corbin, J., \& Strauss, A. (2014). \emph{Basics of qualitative research: Techniques and procedures for developing grounded theory}. Sage publications.

\leavevmode\vadjust pre{\hypertarget{ref-heckel2019pride}{}}%
Heckel, C., \& Ringeisen, T. (2019). Pride and anxiety in online learning environments: Achievement emotions as mediators between learners' characteristics and learning outcomes. \emph{Journal of Computer Assisted Learning}, \emph{35}(5), 667--677.

\leavevmode\vadjust pre{\hypertarget{ref-hernandez2014investigacion}{}}%
Hernandez Carrera, R. M. (2014). La investigacion cualitativa a trav{e}s de entrevistas: Su analisis mediante la teoria fundamentada. \emph{Cuestiones Pedagogicas, 23, 187-210}.

\leavevmode\vadjust pre{\hypertarget{ref-hodges2020difference}{}}%
Hodges, C. B., Moore, S., Lockee, B. B., Trust, T., \& Bond, M. A. (2020). \emph{The difference between emergency remote teaching and online learning}.

\leavevmode\vadjust pre{\hypertarget{ref-horvat2015student}{}}%
Horvat, A., Dobrota, M., Krsmanovic, M., \& Cudanov, M. (2015). Student perception of moodle learning management system: A satisfaction and significance analysis. \emph{Interactive Learning Environments}, \emph{23}(4), 515--527.

\leavevmode\vadjust pre{\hypertarget{ref-ke2013constructs}{}}%
Ke, F., \& Kwak, D. (2013). Constructs of student-centered online learning on learning satisfaction of a diverse online student body: A structural equation modeling approach. \emph{Journal of Educational Computing Research}, \emph{48}(1), 97--122.

\leavevmode\vadjust pre{\hypertarget{ref-lan2010using}{}}%
Lan, Y.-F., \& Sie, Y.-S. (2010). Using RSS to support mobile learning based on media richness theory. \emph{Computers \& Education}, \emph{55}(2), 723--732.

\leavevmode\vadjust pre{\hypertarget{ref-lee2022factors}{}}%
Lee, S.-M. (2022). Factors affecting the quality of online learning in a task-based college course. \emph{Foreign Language Annals}, \emph{55}(1), 116--134.

@@

\leavevmode\vadjust pre{\hypertarget{ref-ruiz2022transitioning}{}}%
Ruiz-Alonso-Bartol, A., Querrien, D., Dykstra, S., Fernández-Mira, P., \& Sánchez-Gutiérrez, C. (2022). Transitioning to emergency online teaching: The experience of spanish language learners in a US university. \emph{System}, \emph{104}, 102684.

\leavevmode\vadjust pre{\hypertarget{ref-teimouri2019second}{}}%
Teimouri, Y., Goetze, J., \& Plonsky, L. (2019). Second language anxiety and achievement: A meta-analysis. \emph{Studies in Second Language Acquisition}, \emph{41}(2), 363--387.

\leavevmode\vadjust pre{\hypertarget{ref-thompson2021attitudes}{}}%
Thompson, A. S. (2021). Attitudes and beliefs. In \emph{The routledge handbook of the psychology of language learning and teaching} (pp. 149--160). Routledge.

\leavevmode\vadjust pre{\hypertarget{ref-tomasik2021educational}{}}%
Tomasik, M. J., Helbling, L. A., \& Moser, U. (2021). Educational gains of in-person vs. Distance learning in primary and secondary schools: A natural experiment during the COVID-19 pandemic school closures in switzerland. \emph{International Journal of Psychology}, \emph{56}(4), 566--576.

\leavevmode\vadjust pre{\hypertarget{ref-ushida2005role}{}}%
Ushida, E. (2005). The role of students' attitudes and motivation in second language learning in online language courses. \emph{CALICO Journal}, 49--78.

\leavevmode\vadjust pre{\hypertarget{ref-webb2014flipping}{}}%
Webb, M., Doman, E., \& Pusey, K. (2014). Flipping a chinese university EFL course: What students and teachers think of the model. \emph{The Journal of Asia TEFL}, \emph{11}(4), 53--87.
